---
title: "Data Mining"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

Load all required packages.

```{r library, include=FALSE}
require("xml2")
library('rvest')
library('NLP')
library('tm')
library('stringr')
library('dplyr')
library("DT")
library("plyr")
```

## Import Data

Import the datasets of country information, GNI per capita (2016), GGI (2016), and SIGI (2014).

```{r import}
# read files
country = read.csv(file.path("datasets", "country.csv"), na.strings=c("", "NA"), sep=",")
gni = read.csv(file.path("datasets", "gni.csv"), na.strings=c("", "NA"), sep=",")
ggi = read.csv(file.path("datasets", "ggi.csv"), na.strings=c("", "NA"), sep=",")
sigi = read.csv(file.path("datasets", "sigi.csv"), na.strings=c("", "NA"), sep=",")
```

## Preprocess Data

Step 1 : Combine datasets *country* and *gni* as *country_gni*.

Step 2 : Extract the overall GGI and SIGI values of each country and combine with *country_gni* as dataset *dta*.

Step 3 : Exclude NA values.

```{r pre}
# process country data
country_gni = merge(country, gni)
country_gni = country_gni[complete.cases(country_gni), ]

# process ggi data
ggi_TOT = subset(ggi, select = c(Country_Name, overall_score))
colnames(ggi_TOT)[2] = "GGI"

# process sigi data
sigi_TOT = sigi[grep("TOT", sigi$Subject), ]
colnames(sigi_TOT)[3] = "SIGI"
sigi_TOT = subset(sigi_TOT, select = -Subject)

# merge datasets
dta = join_all(list(country_gni, ggi_TOT, sigi_TOT), type = "left")
dta = dta[complete.cases(dta), ]

DT:::datatable(
    dta,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=3)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 3)
                  )
              )
```

.

Step 4 : Assign attribute **Region** to dummy variable **MENA**, the value being 1 if the country is in the Middle East & North Africa region, 0 if otherwise.

```{r dummy}
# add dummy variables
dta$MENA = ifelse(dta$Region == "Middle East & North Africa", 1, 0)
```

Step 5 : Compute log value of GNI per capita, standardize GGI and SIGI, add dummies, and assign to new dataframe *df*. 

```{r df}
# create df
df = dta %>%
  summarise(Country_Code = Country_Code, log_GNI=log(GNI_per_capita), GGI_s=(GGI - mean(GGI))/sd(GGI), SIGI_s = (SIGI - mean(SIGI))/sd(SIGI), MENA = MENA)

DT:::datatable(
    df,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=2)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 2)
                  )
              )
```

.

## Export Dataset

Export dataset *df* and save as df.csv.

```{r export, eval=FALSE}
# export df
write.csv(df, "df.csv")
```
