---
title: "Model Building - map2stan"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

Load all required packages.

```{r library, include=FALSE}
library(DT)
library(readr)
library(rstan)
library(rethinking)
library(dplyr)
```

## Fit Model

### Import Data

Import the df dataset.

```{r import}
# read files
df = read.csv(file.path("datasets", "df.csv"))
# trim data frame
df = df[ , c("log_GNI","SIGI_s","MENA")]
```

```{r map, include=FALSE}
# define model fit by map
m1.4 <- map(
  alist(
    log_GNI ~ dnorm(mu, sigma),
    mu <- a + bS*SIGI_s + bSM*SIGI_s*MENA + bM*MENA,
    a ~ dnorm(8,100),
    bS ~ dnorm(0,1),
    bM ~ dnorm(0,1),
    bSM ~ dnorm(0,1),
    sigma ~ dunif(0,10)
  ),
  data <- df)
```

### Fit Models With map2stan

Fit Model 1.4 using Hamiltonian Monte Carlo (map2stan).

```{r map2stan, eval=FALSE}
# define model fit by map2stan
m1.4.stan <- map2stan(
  alist(
    log_GNI ~ dnorm(mu, sigma),
    mu <- a + bS*SIGI_s + bSM*SIGI_s*MENA + bM*MENA,
    a ~ dnorm(8,100),
    bS ~ dnorm(0,1),
    bM ~ dnorm(0,1),
    bSM ~ dnorm(0,1),
    sigma ~ dcauchy(0,2)
  ),
  data <- df)
```
```{r map2stan.2, include=FALSE}
# define model fit by map2stan
m1.4.stan <- map2stan(
  alist(
    log_GNI ~ dnorm(mu, sigma),
    mu <- a + bS*SIGI_s + bSM*SIGI_s*MENA + bM*MENA,
    a ~ dnorm(8,100),
    bS ~ dnorm(0,1),
    bM ~ dnorm(0,1),
    bSM ~ dnorm(0,1),
    sigma ~ dcauchy(0,2)
  ),
  data <- df)
```

### Parameter Overview

Compare map to map2stan to check the quadratic approximation. From the table of coefficients, we can see that the numbers are approximately the same.

```{r coeftab}
coeftab(m1.4, m1.4.stan)
```

For the Stan model and these data, the resulting posterior distribution is quite nearly multivariate Gaussian. 

According to the pairs plot below, the density for sigma is slightly skewed in a certain direction, but otherwise the quadratic approximation does almost as well as Hamiltonian Monte Carlo. Since the quadratic approximation turned out to be okay, we can continue to use map estimates.

Also, since there is nearly no correlation among parameters, we can conclude that each predictor variable provides unique, irreplacable information. Hence, this is a good-fitting model.

```{r stan.pairs}
pairs(m1.4.stan)
```
